% Ben Luersen Resume

\documentclass[margin,line]{resume}

\usepackage{graphicx}

\begin{document}

\name{\huge \sc{Benjamin Luersen}\vspace{2mm}}
{
    \hfill ben.luersen@gmail.com       \vspace{0mm}\\\vspace{0mm}%
    \hfill (859) 802-5263 \vspace{0mm}\\\vspace{0mm}%
    \hfill github.com/benluersen \vspace{0mm}\\\vspace{0mm}
    \hfill linkedin.com/in/benluersen           \vspace{-9mm}\\\vspace{0mm}%
    
}

\begin{resume}

    \vspace{-1mm}

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    \textbf{\textsl{Software Developer}} particularly interested in writing programs that have a \textbf{positive impact} on the world. My love of \textbf{learning} is what drives me to elevate my abilities on a daily basis. Utilizing \textbf{input} from others in tandem with my own \textbf{creativity} provide me with the opportunity to bring interesting and unique \textbf{ideas} to fruition.

    \vspace{1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Education
\vspace{2mm}
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing Tech Elevator}, Cincinnati, Ohio \vspace{1mm}\\
    \textsl{.NET/C\#} \hfill \textbf{September 2019 --Present}\vspace{1mm}\\\vspace{0mm}%
     Currently attending 14-week coding bootcamp learning how to develop dynamic web-based software systems using C\#. \vspace{-5mm}\\

    \textbf{\listing University of Louisville} \vspace{1mm}\\
    \textsl{Philosophy} \hfill \textbf{January 2016 -- May 2018}\vspace{1mm}\\\vspace{0mm}%
     Earned a degree in philosophy which required the solving of complex problems using logic as well as time management and discipline. Relied on my peers' and professors' input to craft creative resolutions to abstract issues. 

    \vspace{1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Skills
\vspace{2mm}
    \section{\mysidestyle \textbf{\large{T}\small{ECHNICAL}  \large{S}\small{KILLS}}}

    \textbf{Backend:} .NET/C\#\vspace{1mm}\\
    \textbf{Frontend:} HTML, CSS, JavaScript, Vue.js\vspace{1mm}\\
    \textbf{Databases:} MS SQ\vspace{1mm}L\\
    \textbf{Version control systems:} Git, Git Bash\vspace{1mm}\\
    \textbf{Misc:} Blender, SAP, Adobe Premier, Adobe Photoshop, SPSS, LaTeX
\vspace{1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Technical Experience
\vspace{2mm}
    \section{\mysidestyle \textbf{\large{T}\small{ECHNICAL} \large{E}\small{XPERIENCE}}}
     \textbf{\listing Vending Machine Software:} \vspace{1mm}\\\vspace{0mm}%
Developed a console application simulating a vending machine including inventory management and action logging using C\#.\vspace{2mm}\\
\textbf{\listing National Park Registration App:} \vspace{1mm}\\\vspace{0mm}%
Developed a console application which allowed users to select and reserve campsites at a national park while taking information from, as well as writing to, a database using C\# and MS SQL Server.\vspace{2mm}\\
	\textbf{\listing Tree Identification App} \vspace{1mm}\\\vspace{0mm}%
Developed a console application allowing the user to identify native trees of Kentucky using leaf characteristics using C\#.

\vspace{1mm}

\sectionline
    %__________________________________________________________________________________________________________________
    % Professional Experience
\vspace{2mm}
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL} \large{E}\small{XPERIENCE}}}

    % *Resnet*
    \textbf{\listing ResNet} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Consultant} \hfill \textbf{August 2011 - December 2015}\\
\begin{description}
  \item[$\cdot$] Troubleshooted hardware, software, and network related problems over the phone.
 \item[$\cdot$] Visited client’s onsight if their concern was unable to be resolved over the phone. 
\item[$\cdot$] Kept accurate, but concise documentation of all operations done to client’s computer. 
\item[$\cdot$] Worked with a team to perform large scale operations. Created documentation to help train future employees.



\end{description}









\end{resume}
\end{document}
